Stat 400 Project

### 2021-11-25 Stat 400 proj.Rmd
Started getting simulator made, still has issues

#Function for deciding if infections occured
infection_status <- function(state, mean_crit_dist){

  current_infected <- state[state[,'subjects']=='I',]
  current_suceptable <- state[state[,'subjects']=='S',]
  current_removed <- state[state[,'subjects']=='R',]

@@

#simulation function
simulator <- function(days, num_subjects, x_dim, y_dim, I_0){
  initial_data <- starting_vals(num_subjects = num_subjects, x_dim=x_dim, y_dim=y_dim, I_0=I_0)

@@

>>>>

#Function for deciding if infections occured
#BUG -- If the mean_crit_dist is small, all infections go away!!
infection_status <- function(state, mean_crit_dist){

  current_infected <- state[state[,3]=='I',]
  current_suceptable <- state[state[,3]=='S',]
  current_removed <- state[state[,3]=='R',]

@@

#simulation function
simulator <- function(days, num_subjects, x_dim, y_dim, I_0){
  initial_data <- starting_vals(num_subjects = num_subjects, x_dim=x_dim, y_dim=y_dim, I_0=I_0)
  end_day <- rep(NA, days)

@@

    if(i == 1){
    step_size <- get_step_length(initial_data, x_dim, y_dim)
    direction <- get_step_direction(step_size)
    change <- get_delts(step_size, direction)
    updated_positions <- update_coords(initial_data, change)
    updated_state <- cbind(updated_positions, initial_data[,3])
    new_status <- infection_status(updated_state, 2)
    end_day[i] <- cbind(updated_positions, new_status)
    }else{
    step_size <- get_step_length(initial_data, x_dim, y_dim)
    direction <- get_step_direction(step_size)
    change <- get_delts(step_size, direction)
    updated_positions <- update_coords(end_day[i-1], change)
    updated_state <- cbind(updated_positions, end_day[i-1]$new_status)
    new_status <- infection_status(updated_state, 1/5)
    end_day[i] <- cbind(updated_positions, new_status)

    }
  }
  return(end_day)
}
